The K2 Bright Star Survey

### 2019-05-17 paper/ms.tex
bedding introduction

% intro kepler
The \kepler Space Telescope was launched with a main goal of determining the frequency of Earth-sized planets around Solar-like stars \citep{2010sci...327..977b}, a goal which it has substantially achieved \citep[e.g.][]{2013ApJ...766...81F,2013PNAS..11019273P,2014ApJ...795...64F}. In order to explore these populations it was necessary to observe hundreds of thousands of stars, with the consequence that the \kepler the exposure time and gain were set to optimally observe eleventh or twelfth-magnitude stars, while bright stars are saturated and these saturated stars were intentionally avoided. In the two-wheeled revival as the \ktwo mission, the \kepler telescope observed a sequence of ecliptic-plane fields containing many more very-saturated stars. While it is difficult to obtain precise light curves of these stars because of their saturation, they are some of the most-valuable targets to follow up with photon-hungry methods such as interferometry or high-resolution spectroscopy, and they typically have long histories of previous observations. Dedicated bright-star space photometry missions such as MOST \citep{most} and the BRITE-Constellation \citep{brite,brite2} use very small telescopes (15 and~20\,cm apertures respectively), and we would prefer to use much larger telescopes such as \kepler (0.95\,m) to obtain higher precision lightcurves.

@@

% briefly intro the halo method and halo literature
In order to recover precise photometry of the brightest stars in \ktwo, we have therefore developed two main approaches, `smear' and `halo' photometry. Smear photometry \citep{Pope2016} uses collateral `smear' calibration data to obtain a 1-D spatial profile with $\sim 1/1000$ of the flux on each CCD. This can be processed recover light curves of stars which were not necessarily conventionally targeted and downloaded with active pixels, because smear data are recorded for all columns. The main disadvantage of this method is that it confuses all stars in the same column, which means that in crowded fields smear light curves tend to be significantly contaminated.

% halo
The more precise method of halo photometry, which is the subject of this paper, uses the broad `halo' of scattered light around a saturated star to recover relative photometry, by constructing a light curve as a linear combination of individual pixel time series and minimizing a Total Variation objective function (TV-min). It has been employed for example on the Pleiades \citep{White2017} and the brightest-ever star on \kepler silicon, Aldebaran \citep{Farr2018}, recovering photometry with a precision nearly that of normally-obtained \ktwo observations of unsaturated stars. Unlike smear, this requires downloading data out to a 12--20~pixel radius around each star, and has accordingly only been possible for stars that were specifically targeted with apertures optimized for this method and for a small number of other stars for which this is fortuitously the case. The pixel requirements for this are sufficiently low that, with the help of the \ktwo Guest Observer office, such apertures were obtained for most of the bright targets from Campaign~4 onwards.

% describe contents of paper: code, catalog, categorization, conclusions
In this Paper we describe numerical experiments testing the TV-min method and extending it to generalizations with different exponents and timescales. We show that the method as previously employed applying standard TV-min is suboptimal, and gain a modest improvement from taking finite differences close to the timescale of \ktwo thruster firings. 
We go on to present complete catalog of long-cadence \ktwo halo light curves, which we have made publicly available. We have employed halo photometry on all stars targeted with appropriate apertures, and have done a preliminary characterization of interesting astrophysical variability. We also document the main changes in the halo data reduction pipeline, \texttt{halophot}, with respect to previous releases. These include oscillating red giants, pulsating and quiet main sequence stars, and eclipsing binaries, many of which are among the brightest objects of their type to have been observed with space photometry. We hope that this diverse catalog of light curves will be useful for an equally-diverse range of astrophysical investigations.

>>>>

% intro kepler
The \kepler Space Telescope was launched with a main goal of determining the frequency of Earth-sized planets around Solar-like stars \citep{2010sci...327..977b}, a goal which it has substantially achieved \citep[e.g.][]{2013ApJ...766...81F,2013PNAS..11019273P,2014ApJ...795...64F}. In order to explore these populations it was necessary to observe hundreds of thousands of stars, with the consequence that the \kepler exposure time and gain were set to optimally observe eleventh or twelfth-magnitude stars, while bright stars are saturated and intentionally avoided. In the two-wheeled revival as the \ktwo mission, the \kepler telescope observed a sequence of ecliptic-plane fields containing many more very-saturated stars. While it is difficult to obtain precise light curves of these stars because of their saturation, they are some of the most-valuable targets to follow up with photon-hungry methods such as interferometry and high-resolution spectroscopy, and they typically have long histories of previous observations. Dedicated bright-star space photometry missions such as MOST \citep{most} and the BRITE-Constellation \citep{brite,brite2} use very small telescopes (15 and~20\,cm apertures respectively), and we would prefer to use much larger telescopes such as \kepler (0.95\,m) to obtain higher precision lightcurves.

@@

% briefly intro the halo method and halo literature
In order to recover precise light curves of the brightest stars in \ktwo, we have therefore developed two main approaches, `smear' and `halo' photometry. Smear photometry \citep{Pope2016} uses collateral `smear' calibration data to obtain a 1-D spatial profile with $\sim 1/1000$ of the flux on each CCD. This can be processed recover light curves of stars that were not necessarily conventionally targeted and downloaded with active pixels, because smear data are recorded for all columns. The main disadvantage of this method is that it confuses all stars in the same column, which means that in crowded fields smear light curves tend to be significantly contaminated.

% halo
The more precise method of halo photometry, which is the subject of this paper, uses the broad `halo' of scattered light around a saturated star to recover relative photometry, by constructing a light curve as a linear combination of individual pixel time series and minimizing a Total Variation objective function (TV-min). It has been employed for example on the Pleiades \citep{White2017} and the brightest-ever star on \kepler silicon, Aldebaran \citep{Farr2018}, recovering photometry with a precision close to that normally obtained from \ktwo observations of unsaturated stars. Unlike smear, this requires downloading data out to a 12--20~pixel radius around each star, and has accordingly only been possible for stars that were specifically proposed and targeted with apertures optimized for this method, plus a small number of other stars for which this is fortuitously the case. The pixel requirements for this are sufficiently low that, with the help of the \ktwo Guest Observer office, such apertures were obtained for most of the bright targets from Campaign~4 onwards.

% describe contents of paper: code, catalog, categorization, conclusions
In this Paper we describe numerical experiments testing the TV-min method and extending it to generalizations with different exponents and timescales. We show that the method as previously employed applying standard TV-min is suboptimal, and gain a modest improvement from taking finite differences close to the timescale of \ktwo thruster firings. We also document the main changes in the halo data reduction pipeline, \texttt{halophot}, with respect to previous releases. 
We go on to present complete catalog of long-cadence \ktwo halo light curves, which we have made publicly available. We have employed halo photometry on all stars targeted with appropriate apertures, and have done a preliminary characterization of interesting astrophysical variability. These include oscillating red giants, pulsating and quiet main sequence stars, and eclipsing binaries, many of which are among the brightest objects of their type to have been observed with space photometry. We hope that this diverse catalog of light curves will be useful for an equally-diverse range of astrophysical investigations.
